---
title: 'EDA: Finding COVID-19'
output:
  html_document:
    df_print: paged
---

# Abstract

This exploratory data analysis notebook continues from the [Novel Coronavirus (COVID-19) Cases from a South African perspective](https://github.com/willkhoza/COVID_SA) repository. The purpose of this analysis is to understand the influence of demographic settings on the early progression of the COVID-19 within different countries.


# Introduction
## Data Dictionary

Albeit the demographic variables being intuitively named, a detailed data dictionary is provided in the [worldometer](https://github.com/willkhoza/COVID_SA/tree/master/worldometer) folder in the repository.

The following variables are defined:

$t_1$: The amount of days it takes for a country to report it's **first confirmed case** with a base date of 17 November 2019. This base date has been unofficiially reported to be the earliest detected case of the disease.

$t_2$: The amount of days it takes for a country to report it's **first death** which relates COVID-19.

## Correlogram and Regression Plots



```{r, include=FALSE, code = readLines("01_read_data.R")}
```

```{r, message = FALSE, echo = F,warning=FALSE, code = readLines("02_exploratory_data_analysis.R")}
```

