---
title: 'Annexure 1: COVID-19 early days regression analysis'
output:
  word_document: default
  html_document:
    df_print: paged
---

#### Lindo Khoza


# Background

This exploratory data analysis notebook continues from the [Novel Coronavirus (COVID-19) Cases from a South African perspective](https://github.com/willkhoza/COVID_SA) repository. The purpose of this analysis is to understand the influence of demographic settings on the early progression of the COVID-19 within different countries.


## Data Dictionary

Albeit the demographic variables being intuitively named, a detailed data dictionary is provided in the [worldometer](https://github.com/willkhoza/COVID_SA/tree/master/worldometer) folder in the repository.

The following variables are defined:

$t_1$: The amount of days it takes for a country to report it's **first confirmed case** with a base date of 17 November 2019. This base date has been unofficiially reported to be the earliest detected case of the disease.

$t_2$: The amount of days it takes for a country to report it's **first death** which relates COVID-19.

## Data Summary

```{r, message = FALSE, warning=FALSE, code = readLines("01_read_data.R")}
```

## Correlogram and Regression Plots

```{r, message = FALSE,warning=FALSE, code = readLines("02_exploratory_data_analysis.R")}
```

## $t_1$: Regression Analysis

```{r, message = FALSE, warning=FALSE,code = readLines("03_regression_models_t1.R")}
```


## $t_1$: Decision Tree Analysis

```{r, message = FALSE, warning=FALSE,code = readLines("04_tree_model_t1.R")}
```


## $t_2$: Regression Analysis

```{r, message = FALSE, warning=FALSE,code = readLines("05_regression_model_t2.R")}
```

